\section{Discussion}

Our analysis is the first attempt to estimate the relative contributions of \textit{in situ} lineage diversification and colonization to the assembly of one of the world's richest temperate floras, that of the Hengduan Mountains. We expected regional differences to reflect contrasting times of orogeny; in particular, the prediction of the uplift-driven diversification hypothesis that \textit{in situ} speciation increases with mountain-building activity. In this context, the late Miocene emerges as an important reference point, as previous studies of geology and paleontology indicate that the Hengduan Mountains achieved their current height only after this time, while the Himalayas and central QTP did so before (REFS). Here, our phylogenetic inferences, which make no prior assumptions about the timing of geological events, show that after about 8 Ma, the rate of \textit{in situ} diversification increased in the Hengduan Mountains, yielding a remarkable inflection point at which cumulative speciation overtakes colonization. This indicates that the Hengduan Mountains flora has been assembled disproportionately by recent \textit{in situ} diversification that coincides temporally with independent estimates of orogeny, and is the first quantitative evidence consistent with the uplift-driven diversification hypothesis.

We do not find a similar signature of accelerated \textit{in situ} diversification for the Himalayas-QTP region, as might be expected from rapid Himalayan orogeny during the early to middle Miocene (REFS: Searle 2011?)  % \citep{WangY2007,Mao2010}
. It is possible that no such pulse of diversification occurred, e.g., if uplift of the Himalayas was more gradual. Alternatively, we could simply lack the statistical power to detect it, due to the masking effects of treating the older QTP and the younger Himalayas as a single region, the greater uncertainty associated with estimating clade ages and ancestral ranges in deeper time, and/or extinction and turnover in the Himalayas-QTP flora.

% From Fig.2, speciation rate of Himalayas also increased until around 8 Ma, and keep constant since then. This probably due to Himalayas already reached its current elevation.

%Surpringly, our results indicate Himalayas-QTP flora was assembled later (Fig **). Ideally, bring paleontological evidence to bear on assembly/diversification questions - but the record is sparse. The exact time of onset of current biome remains unclear.

% MAIN POINT: temporal shifts (increases) in diversification in the absence of statistically significant endemic radiations

Given the inferred rise in \textit{in situ} diversification in the Hengduan Mountains since the late Miocene, the overall lack of evidence for macroevolutionary jumps in diversification rate associated with colonization of the region might seem surprising. However, across our phylogenies, dispersal is relatively frequent and clades tend not to be entirely endemic to a single region. This reflects the fact that our regions are not, in general, defined by differences in biome; the Hengduan Mountains, Himalayas, and QTP share broad physiographic similarities that presumably have facilitated biogeographic exchange. That is, dispersal between these regions should not necessarily require extensive ecophysiological adaptations that may be difficult to evolve \citep{Donoghue2014}, countering expectations of infrequent colonization events followed by endemic radiations \citep[cf.][]{Hughes2006}. For this reason our data are perhaps not well-suited for BAMM, which models diversification shifts as relatively rare events. Moreover, the link between dispersal events and shifts in diversification regime is further obscured by the inherent uncertainty associated with inferring their phylogenetic locations. The most appropriate interpretation may simply be that the signal of higher diversification in the Hengduan region is more or less diffuse across clades, and emerges only when their biogeographic histories are considered jointly. This helps explain why previous analyses of single clades have not yielded the pattern inferred here.

%\textbf{Drivers of Hengduan diversification.}---
Why did \textit{in situ} diversification in the Hengduan Mountains increase since the late Miocene, and more specifically, to what extent was it driven by orogeny? Further studies are needed. One might look for contrasts between the Hengduan Mountains and adjacent regions in the evolution of ecological traits and environmental tolerances \citep[e.g.,][]{liu2016} across multiple clades. These may reveal, for example, the extent to which speciation within a region is associated with adaptive divergence and niche-filling, as opposed to nonadaptive processes such as genetic isolation and drift arising from dispersal limitation and topographic effects (vicariance, emergence of sky islands, etc.). These analyses would require denser and more fine-grained taxonomic and geographic sampling than was possible here, in addition to the requisite trait data.

% Aridification and global cooling as a result of orogeny (see reviews in \citealt{MiaoY2012}) may be an important factor influencing the diversification of plants on the QTP.

We suspect that evidence for common processes will prove elusive, as the proximate causes of diversification are likely to be idiosyncratic. For many clades, factors unrelated to uplift \emph{per se}, such as biotic interactions, are almost certain to have played important roles \citep{Luebert2014,Wen2014,Renner2016}. For example, in \emph{Pedicularis} (Orobanchaceae), diversification of the many Hengduan species may have been facilitated by recurrent divergence in floral traits associated with pollinator sharing and reproductive interference \citep[e.g.,][]{eaton2012}.

A coarser-grained view is that diversification in the Hengduan region reflects a macroevolutionary response to the rapid expansion of moist temperate montane and alpine habitats in the late Miocene. At this level the effects of orogeny and climate change are not clearly separable, as they concurrently and jointly set a stage of ecological/evolutionary opportunity. During the early to middle Miocene, the southern QTP had already achieved its current elevation \citep{Spicer2003} and was covered by coniferous and deciduous-leaved forests \citep{SunJ2014,LiH1976}% , and limited paleobotanical evidence suggests that the entire Himalayas-QTP region may have experienced a dramatic shift in vegetation after the middle Miocene
. As Hengduan uplift proceeded, falling temperatures would have driven the treeline lower, increasing the extent of shrublands, meadows, and scree slopes---habitats where most of the species in our data set occur and would have diversified. Similar changes would also have occurred in the Himalayas and QTP, but in comparison to those areas, moisture in the Hengduan region would have been abundant, as by then, the summer monsoon was established, and the central QTP and Central Asian interior had aridified \citep[see][]{Renner2016}. This predicts that carrying capacities---and by extension, diversification potential---of the Hengduan region's newly formed habitats were enhanced by greater summer rainfall. 

% Accounting for the effect of Pleistocene climate fluctuations

While not a driver of diversification \textit{per se}, it is important to consider the effects of glaciation and climatic oscillations during the Pleistocene, and the possibility that our results can be explained, at least in part, by regional differences in extinction caused by these factors. If the Hengduan region had more Pleistocene refugia, we would expect its history of \textit{in situ} diversification to be better preserved in time-calibrated phylogenies, simply because fewer branches would have been ``pruned'' by extinction. By contrast, greater extinction in the Himalayas-QTP, if phylogenetically random, would tend to erase nodes representing recent \textit{in situ} speciation events, and increase the average nearest-phylogenetic-neighbor distance for pre-Pleistocene resident survivors. That is, even if regional rates of \textit{in situ} diversification were equal up to the Pleistocene, we might infer the rate to be higher in the region that experienced less Pleistocene extinction.

Numerous studies of species distributions \citep[e.g.,][]{srinivasan2014,lopez2011} and phylogeography \citep[e.g.,][]{CunY2010,WangBS2011,lei2014,meng2015} support the idea that refugia were concentrated along the southeastern margin of the QTP, but also occurred in areas further west and north, even at high elevation \citep[e.g.,][]{wang2009,sun2010,opgenoorth2010}. This aligns with geological evidence that ice-free areas were present across the QTP and adjacent mountains throughout the Quaternary \citep[see][]{owen2014}. It may be that greater Pleistocene extinction in the Himalayas-QTP compared to the Hengduan region was driven as much (or more) by aridification as glaciation, during periods of reduced summer monsoon strength associated with local interglacials \citep{owen2008}.

These effects may be reflected in temporal patterns of dispersal between the Hengduan Mountains and Himalayas-QTP. The older age of the latter predicts that its flora should have been an early source of lineage dispersal to the younger Hengduan Mountains. However, we do not find any marked asymmetry in dispersal between these regions through the end of the Miocene; instead, rates in both directions are relatively low and increase only gradually until about 2--3 Ma, when both increase more sharply, but more so from the Hengduan Mountains to the Himalayas-QTP (Fig.~\ref{fig:dispersal}). That is, in the Quaternary, the Hengduan Mountains appear to have acted as a biogeographic source, from which lineages buffered from extinction colonized the relatively depauperate regions to the west and north. % This may reflect phylogeographic evidence that the Hengduan Mountains flora was likely buffered from extinction during Quaternary glacial cycles, with subsequent westward range expansion/recolonization of the Himalayas and QTP \citep[e.g.,][]{WangBS2011,CunY2010}. 

% even paleoelevational recontruction suggesting this regions already reached their current elevation by then . The onset and diversification of alpine biome may be much later than the uplift.

% More generally, it seems reasonable to view uplift and climate change as primary drivers of expanding ecological opportunities for temperate-montane species in the Hengduan region in the late Miocene.

%\textbf{Comparisons to other taxa, mountains, and hotspots.}

Other than plants, the group that has received the most biogeographic scrutiny in relation to the QTP and adjacent regions is birds, which present similar patterns \citep[see][]{packert2015}, notably that in the species-rich Hengduan Mountains region and adjacent forests of SE Asia, \textit{in situ} diversification during and subsequent to the Miocene led to repeated colonization of the Himalayas and QTP \citep[e.g.,][]{liu2016,tietze2013,johansson2007}. In the Himalayas, the lack of \textit{in situ} diversification of songbirds has been attributed to the filling of niches by pre-adapted colonizing lineages \citep{price2014}.

% In this study we attempt to place the Hengduan Mountains flora in historical biogeographic context through the joint analysis of representative clades. The picture that emerges is one in which \textit{in situ} diversification accelerates relative to colonization around the time orogeny is believed to have started.

% To what extent do our results reflect general features of how biodiversity hotspots, especially those associated with mountains, are assembled?

% In this study we analyze the assembly of a biodiversity hotspot using a comparative framework of 4 dimensions: tempo (rates of biogeographic events), mode (\textit{in situ} diversification versus colonization), time

In a recent review, \citet{Renner2016} argued that numerous phylogenetic studies have misinterpreted the Earth sciences literature and incorrectly attributed relatively young (Miocene and later) estimates of lineage divergence to QTP uplift, and recommended that ``Biogeographical discussions should also keep in mind expected differences in the biota of the TP and those in the Himalayas, the Kunlun range to the N, the Pamir and Karakoram to the W, and Hengduan Mountains to the E'' \citep[][p.~7]{Renner2016}. Here, our focus on distinguishing the younger and more species-rich Hengduan Mountains region from the Himalayas-QTP is in the spirit of that advice, and our results suggest that at least some of the referenced cases of diversification could be more accurately interpreted as coincident with orogeny of the Hengduan region, not the older QTP. Indeed, several of the studies cited in \citet{Renner2016} are the original sources of molecular data for the clades analyzed here (see Supporting Information), and include many Hengduan species. It thus seems important to emphasize that, despite precedent in the literature for considering the Hengduan Mountains to be simply part of a greater biogeographic region that includes the Himalayas and QTP \citep[e.g.][]{Zhang2014,Nie2013,GaoY2013,Matuszak2016}, the Hengduan region actually has a very distinct history of assembly that reflects its younger age.

Among studies inferring biodiversity hotspot assembly from multiple clades, quantitative analyses of \textit{in situ} diversification and/or colonization are still rare, and ours is the first to estimate rates of both processes through time and across regions. This comparative framework has allowed us to characterize, at a very basic level, changes in the tempo (rate) and mode (process) of biotic assembly in relation to independently-inferred timelines of regional orogeny and climate change. By contrast, studies of other hotspots have tended to focus on single regions or biomes, and subsets of these dimensions (time, space, tempo, and mode). For example, the high species diversity in the California Floristic Province is associated with lower rates of extinction more than elevated speciation or immigration, using models in which rates of lineage birth, death, and movement are dependent on geographic occupancy but not time \citep{lancaster2013}. In the Páramo biome of the Andes, analyses of net diversification (but not immigration) of resident plant clades yielded the highest average rate compared to clades in eight other hotspots, and appears driven more by Pleistocene climate oscillations than orogeny \citep{Madrinan2013}. Assembly of the Cerrado biome is characterized by recent (late Miocene onwards) colonization events associated with adaptations to fire resistance, but not extensive \textit{in situ} diversification \citep{simon2009}. Clearly, for the Hengduan Mountains, much remains to be studied about how patterns of assembly through time break down at a finer scale of particular biomes and habitats within the region.

The validity of our results hinges on the degree to which the data are representative of the focal regions (Hengduan Mountains and Himalayas-QTP). The clades we selected span a wide taxonomic range, and the species exhibit a diversity of growth forms, life histories, and habitat preferences. Taxon sampling, while incomplete, is not generally biased with respect to the focal regions (REF:Table S1), and therefore should not unduly affect inferences of the relative rates of assembly processes across regions. We also expect the phylogenetic distribution of unsampled species within each clade to be effectively random, which means that reconstructed phylogenies would tend to be missing more nodes---and thus inferred biogeographic events---closer to the present. In other words, the extent to which we have underestimated the frequencies of those events is likely greater in the Pliocene and Quaternary than in the Miocene and earlier.

The decision to consider the Himalayas and QTP as a single biogeographic region for the purpose of estimating ancestral ranges, when it is clear they have distinct geological histories, is a valid criticism of our study. However, to place the biogeographic assembly of the Hengduan Mountains in a global context, it was necessary to adjust the granularity of the geographic coding of species ranges to the resolution of available raw data, which often did not differentiate the Himalayas from the QTP. While clearly suboptimal, it does not obscure the main distinction of interest, namely the younger age of the Hengduan Mountains.

% MAIN POINT: higher species diversity need not, and should not be expected to, reflect older orogeny (cf. Mutke et al.). Younger mountains: more diverse?

% MAIN POINT: hotspots are functions of climate stability (refugia) during the Pleistocene, and opportunity for in situ diversification during the Miocene/Pliocene



% In the Introduction, we considered the processes of \textit{in situ} diversification and colonization as equally likely a priori to contribute to the assembly of biodiversity hotspots. We find that diversification wins. The question then becomes: is this a general result, or specific to the unique circumstances of the Hengduan Mountains, and therefore unpredictable?

% \textit{In situ} diversification also implicated in the assembly of other biodiversity hotspots: the Andes, California Floristic Province (Kay and Lancaster?), Cape Floristic Region? Uplift-driven diversification: Andes, Japan?

% How is the Hengduan Mountains region similar to other biodiversity hotspots? How does it differ? The Hengduan Mountains region is a young biodiversity hotspot. Young hotspots contradict the general expectation that diversity is a function of time (Fine and Ree).

% Comparison to paramo study: net diversification only, no dispersal; how did they define ``paramo'' clades (and clades of other hotspots)?

% Comparison with northern Andes: both are young mountain regions. May reveal general properties of uplift-driven diversification.

% General considerations: ecological opportunities. Age, area, and environmental factors (moisture, temperature, seasonality, soil characteristics) influencing energy-diversity expectations.

% Age: Hengduan Mountains are young; within it, alpine biome even younger

%  extant diversity, and historical diversification (to the extent it can be inferred), reflects regional carrying capacities through time. 

% An important consideration in this context is climatic conditions over time---moisture and temperature in particular---that influence primary productivity,  

% Density-dependent effects: Himalayas are older, are niches more filled relative to Hengduan Mountains?

% Pleistocene effects: differential extinction. Young clades: Saussurea

% Perenniality, woodiness are something like ``classic'' traits associated with alpine radiation (Hughes and Atchison) - but our clades include many herbaceous species. Hybridization (Rhododendron: Milne). Sky islands (e.g., Solms-Laubachia): does population isolation lead to the proliferation of narrow endemics (that are more prone to extinction)?

% Younger clades like Saussurea - ecological opportunity of new alpine habitat?

% Predict that earliest clades are montane, most recent radiations are alpine. Not entirely the case. Pinaceae, Acer, Delphineae are montane, and colonize early. Alpine clades like Saussurea and Ligularia colonized later and with exeptional high rates (Saussurea has crown age c. 3 Myr, but has generated more than 400 species). But Meconopsis(true???), Saxifragaceae, and Polygoneae have many alpine members (Saxifragaceae and Polygoneae include many montane even low land species as well), and are the earliest clades to accumulate \textit{in situ} speciation events in the Hengduan Mountains.

% Notably, clades that occur primarily in the relatively arid alpine zone, such as \textit{Saussurea} and \textit{Rhodiola}, show faster diversification in the past 10 Ma than montane clades such as Primulaceae (s.s.) and \textit{Cyananthus}. However, precipitation is not a limiting factor in north-south-going Hengduan Mountains since moist air from the Indian Ocean can go through by the valleys, facilitating diversification of montane clades like \textit{Rhododendron} and Primulaceae (s.s.). 

% Early uplift of the plateau: what was the biome of the proto-QTP during the Eocene, Oligocene---presumably forests? Lagrange reconstructions of Hengduan (and Himalayan) ancestry that pre-date the origins of these mountains may indicate high-elevation ancestors

% how old is the alpine biome in HM, Him? Prediction: alpine flora: young species, recent colonists

% Uplift-driven diversification is either a too-simplistic hypothesis that fails to acknowledge the numerous other factors that likely contribute to biological diversification in mountains, or a too-vague catchall phrase that encompasses them all.

% Here we have found temporal alignment of elevated diversification and orogeny, with evidence coming from the joint analysis of many clades, which suggests that uplift may have had a general effect.

% Rapid evolutionary radiations of plants have been documented in most major mountain ranges worldwide \citep[reviewed in][]{Hughes2015}, including the European Alps \citep{Roquet2013}, Andes \citep[e.g.][]{Hughes2006,Luebert2014}), Rocky Mountains \citep{DrummondC2012}, New Zealand \citep{Joly2014}, and the East African Rift mountains \citep{Linder2014}. Most of these have been dated to the last 5 Ma, conciding with or occurring much later than orogeny. Apparently, the Hengduan mountain radiation is older dating back to 8--10 Ma. Andes is comparable with the Himalayas-QTP and the Hengduan mountains in several ways. They habor the most alpine diversity among the mountain ranges. The initial uplift of Andes and QTP dated back to late Eocene \citep{Gregory-Wodzicki2000,Graham2009}, but plant radiations are more influenced by recent uplift (late Miocene and onwards) \citep{Hughes2013,Luebert2014,Hughes2015,Madrinan2013}. \citet{Hughes2013} pointed out that different biomes in the Neotropics may have different evolutionary histories. It is probably the case in the Himalayas-Hengduan Mountains as well. 

%\textbf{Sources of error and bias.}


%%% Local Variables:
%%% mode: latex
%%% TeX-master: "master"
%%% End:
