\section*{Results}

\subsection*{Contrasting histories of floristic assembly}

Reconstructed biogeographic histories of the selected clades reveal
distinct patterns of floristic assembly across regions when plotted as
the cumulative number of colonization and \textit{in situ} speciation
events through time (Fig.~\ref{fig:cumevents}). Given geological and
paleontological evidence that the Hengduan Mountains are younger than
the Himalayas-QTP, we expected to find that its flora was assembled
more recently. Instead, we found surprisingly deep phylogenetic
histories of Hengduan occupancy, with initial assembly of its flora
pre-dating that of the Himalayas-QTP. In more than 95\% of the
pseudoreplicated joint histories, the earliest colonization event
occurs by 64 Ma for the Hengduan Mountains and by 59 Ma for the
Himalayas-QTP; \textit{in situ} speciation begins later, starting by
34 Ma and 19 Ma, respectively. By contrast, in East Asia, which was
commonly reconstructed as the root ancestral area for clades,
\textit{in situ} speciation initially occurs by 155 Ma and
colonization initially occurs by 60 Ma.

For all regions, species accumulation by each process is approximately
exponential (log-linear) following initiation until about the last 8
Ma. During this earlier "constant" phase, assembly in both the
Hengduan Mountains and Himalayas-QTP is dominated by colonization,
while in temperate/boreal East Asia the dominant process is \textit{in
  situ} speciation. Following this phase, the assembly dynamics of the
Hengduan Mountains and Himalayas diverge considerably, with relatively
little change in temperate/boreal East Asia. In the Hengduan
Mountains, the cumulative number of \textit{in situ} speciation events
overtakes that of colonization around 8 Ma, and by the present, the
median number is 508 versus 335. In the Himalayas-QTP, \textit{in
  situ} speciation never overtakes colonization, and by the present
the median number of events is 192 versus 411. The relative
contribution of \textit{in situ} speciation to floristic assembly is
thus $508/(508+335) = 0.603$ for the Hengduan Mountains, and
$192/(192+411) = 0.318$ for the Himalayas-QTP. In other words,
\textit{in situ} speciation has contributed almost twice as much to
the assembly of the Hengduan Mountains flora as it has to the
Himalayas-QTP flora, especially since the late Miocene.

\subsection*{Regional rates of \textit{in situ} speciation and
  dispersal through time}

The rate of \textit{in situ} speciation for the Hengduan Mountains
region, in events per resident lineage per Ma, increased almost
twofold over the past 10 Ma, while for the Himalayas-QTP, it remained
more or less constant (Fig.~\ref{fig:speciation}). Dispersal rates
between the Hengduan Mountains and Himalayas-QTP increase gradually
over the last 4--5 Ma, and sharply in the last 1 Ma. By contrast,
dispersal from each region to temperate/boreal East Asia increases
only slightly in the same time period (Fig.~\ref{fig:dispersal}).

\subsection*{Shifts in diversification rate}

Seven out of the 19 clades showed strong evidence (Bayes factor > 15)
for one or more shifts in diversification regime
(Table~\ref{table:bammbayesfactors}). However, inspection of
branch-specific evidence (the cumulative probability of occurring in
the credible set of shift configurations, and the marginal odds ratio
in favor of a shift) in light of ancestral-range reconstructions does
not reveal any clear geographic patterns in the phylogenetic locations
of regime shifts (Fig.~S2). That is, across clades, macroevolutionary
jumps in diversification rate are not obviously associated with the
colonization or occupancy of any particular region.

A notable exception to this general pattern is \emph{Rhododendron}, in
which results from BAMM and Lagrange suggest that in a window of about
9--15 Ma, net diversification increased independently in 2 clades that
each originated in the Hengduan region and are currently dominated by
Hengduan species (Fig.~\ref{fig:rhododendron}). In \emph{Saussurea},
an increase in net diversification is inferred about 1.7 Ma along the
stem of a branch containing most of the clade's Hengduan species
(Fig.~S2O). Similarly, in Delphineae, 2 separate increases are
inferred in clades that are ancestrally Hengduan and together hold
most of the Hengduan species; however the times of these rate shifts
(about 28 Ma and 37 Ma, respectively) pre-date the uplift of the
Hengduan Mountains (Fig.~S2D). Finally, in \emph{Isodon} and the
\emph{Ligularia-Cremanthodium-Parasenecio} complex, branch-specific
measures show one increase in net diversification for each clade in
the context of Hengduan ancestry about 7 and 5 Ma, respectively, but
in both cases, models with regime shifts are not supported by Bayes
factors, and the Hengduan Mountains region is reconstructed as
ancestral across most of the phylogeny, rendering the geographic
context of the shift less informative.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "master"
%%% End:
