\section{Discussion}

Our analysis is the first to make quantitative inferences about the relative contributions of \textit{in situ} lineage diversification and colonization to the assembly of one of the world's richest temperate floras. Despite precedent in the literature for considering the Hengduan Mountains and Himalayas to be a single biogeographic region (e.g. \citealt{Zhang2014,Nie2013,GaoY2013,Matuszak2016}), we find that these regions actually have very distinct histories of assembly. We expected their differences to reflect contrasting times of orogeny: in particular, the uplift-driven diversification hypothesis predicts that \textit{in situ} speciation increases with mountain-building activity.

In this context the late Miocene (10-5 Mya)（**12-8 Mya???**) is an important reference point, as previous studies of geology and paleontology indicate that the Hengduan Mountains achieved their current height only after this time, while the Himalayas did so before. Our neontological analyses show that after about 8 Ma, the rate of \textit{in situ} speciation increased in the Hengduan Mountains, resulting in a remarkable inflection point at which cumulative \textit{in situ} speciation overtakes colonization. This suggests that the Hengduan Mountains flora has been assembled disproportionately by recent \textit{in situ} speciation that coincides temporally with rapid orogeny, supporting the uplift-driven diversification hypothesis. We do not find a similar signature of accelerated \textit{in situ} speciation for the Himalayas corresponding with an earlier period of rapid uplift \citep{WangY2007,Mao2010}. This suggests that Himalayan orogeny was more gradual, and/or that our statistical inferences lack sufficient power, due to the increasing uncertainty in clade age estimates and ancestral state reconstructions in deeper time. % Orogenic caused aridification (see reviews in \citealt {MiaoY2012}) may be an important factor that limiting plant diversification on the palteau.Notably, only real arid-adapted alpine clades like \textit{Saussurea} and \textit{Rhodiola} show rapid diversification in the past 10 Myr, while montane clades such as Primulaceae (s.s.) and \textit{Cyananthus} even show slow-downs in speciation rates. However, precipitation is not a limiting factor in north-south-going Hengduan Mountains since moist air from the Indian Ocean can go through by the valleys which fascinate diversification of montane clades like \textit{Rhododendron} and Primulaceae (s.s.). 

The older age of the Himalayas predicts that its flora was assembled first and acted as a source of lineage dispersal, while the younger Hengduan Mountains acted as a colonization sink. %Surpringly, our results indicate Himalayas-QTP flora was assembled later (Fig **). Ideally, bring paleontological evidence to bear on assembly/diversification questions - but the record is sparse. The exact time of onset of current biome remains unclear. Limited paleontological evidence show that Himalayas-QTP may have experienced a dramatic species/vegetation shift after the middle Miocene. During the early to middle Miocene, southern QTP was still covered by conifer and deciduous-leaved forests \citep{SunJ2014,LiH1976} even paleoelevational recontruction suggesting this regions already reached their current elevation by then \cite{Spicer2003}. The onset and diversification of alpine biome may be much later than the uplift.   
we infer roughly equal rates of dispersal between regions until only the last 1--2 Ma, when dispersal from the Himalayas to the Hengduan Mountains increases more than the converse. That the rate of dispersal from the Hengduan Mountains to the Himalayas increases in the last 4--5 Ma suggests that the Hengduan Mountains began acting as a biogeographic source of lineages around the same time as its formation. %Several phylogeographical studies have suggested that the Hengduan mountains were less affected by the glacier and an east-to-west dispersal route were found in several clades during the Quaternary (e.g. \citealt{WangBS2011,CunY2010}). 


Sources of possible error and bias. Taxon sampling: incomplete, and in some cases not geographically representative (Saxifragaceae). However, our focus is on relative dynamics: comparing \textit{in situ} speciation to colonization (not absolute rates of either process) and comparing the Hengduan Mountains to the Himalayas, and both to the rest of temperate East Asia. So we generally expect the results to be unbiased with respect to our hypotheses.



Comparable analyses of other regions. \textit{In situ} diversification also implicated in the assembly of other biodiversity hotspots: the Andes, California Floristic Province (Kay and Lancaster?), Cape Floristic Region? Uplift-driven diversification: Andes, Japan? % In addition to the Hengduan mountains and Himalayas, rapid plant radiations have been documented in most of major mountain ranges world wile (see reviews in cite\{HughesC2015}), including the Alps \cite{Roquet2013}, Andes (e.g. \citalt{Hughes2006,Luebert2014}), Rockies \cite{DrummondC2012}, New Zealand \cite{Joly2014}, and the East African rift valley mountains \cite{Linder2014}. Most of the radiations are in the last 5 Ma conciding or much later than the mountain uplift. Apparently, the Hengduan mountain radiation is older dating back to 8--10 Ma. Andes is comparable with the Himalayas-QTP and the Hengduan mountains in several ways. They habor the most alpine diversity among the mountain ranges. The initial uplift of Andes and QTP dated back to late Eocene \citep{Gregory-Wodzicki2000,Graham2009}, but plant radiations are more influenced by recent uplift (late Miocene and onwards) \citep{Hughes2013,Luebert2014,HughesC2015,Madriñán2013}. Hughes et al. \cite{HughesC2013} pointed out that different biomes in the Neotropics may have different evolutionary histories. It is probably the case in the Himalayas-Hengduan Mountains as well. ""Which clades colonized first? Predict that earliest clades are montane, most recent radiations are alpine. Not entirely the case. Pinaceae, Acer, Delphineae are montane, and colonize early. Alpine clades like Saussurea and Ligularia colonized later and with exeptional high rates (Saussurea has crown age c. 3 Myr, but generated more than 400 species). But Meconopsis(true???), Saxifragaceae, and Polygoneae have many alpine members(Saxifragaceae and Polygoneae include many montane even low land species as well), and are the earliest clades to accumulate \textit{in situ} speciation events in the Hengduan Mountains." 
